\blue{Numerical Investigation of Multi-Fluid Flows through Dual Saturated-Unsaturated Porous Media - change the title to something close to the main topic of the manuscript ... something with viscous flow instability or viscous fingering)}

### 2017-05-09 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
Updates: working on section 2 now. Figures still floating in the desktop, though working fine in my laptop, thus decided to introduce pic by pic untill find the problem.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\section{Brief Overview of Viscous Instabilities}\label{section:ViscousInstabilities}
\medskip
As in many areas of fluid mechanics, the behaviour of the flow for conditions that exceed critical limits may cause instabilities in the system. The flow of a fluid over or next to another heavier fluid, can produce flow instabilities. Under this assumption when a fluid is injected in a porous domain saturated with another fluid trying to displace it, viscous fingering will occur, as viscous driven hydrodynamic instability leads to the collapse of the uniform interface between fluids of different viscosity. This type of instability can be found across many research areas, disciplines and scales, from small chemical and medical separation systems to large scale field geological and /or reservoir systems. Starting from the work of \citet{muskat_1934} and later from \citet{saffman_1959} and \citet{homsy_1987}, the experimental setup of Hele-Shaw cell by \citet{saffman_1986}, and the basic mathematical model has been initially developed to describe the physics of this phenomenon. The idea is to introduce a fluid between two parallel flat plates separated by an infinitesimally small gap. The governing equation of Hele-Shaw flows is identical to that of the inviscid potential flow and to the flow of fluid through a porous medium (Darcy's law). More recently work that has been done by \citet{howison_2000} and \citet{praud_2005} give an extensive description on the mathematical background of the Saffman $\&$ Taylor problem (also know as immiscible two-phase flow in Hele-Shaw cell).

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\section{Brief Overview of Viscous Instabilities}\label{section:ViscousInstabilities}
\medskip
As in many areas of fluid mechanics, the behaviour of the flow for conditions that exceed critical limits may cause instabilities in the system. The flow of a fluid over or next to another heavier fluid, can produce flow instabilities. Under this assumption when a fluid is injected in a porous domain saturated with another fluid, viscous fingering may occur, as viscous driven hydrodynamic instability leads to the collapse of the uniform interface between fluids of different viscosity.

This type of instability can be found across many research areas, disciplines and scales, from small chemical and medical separation systems to large scale field geological and /or reservoir systems. Starting from the work of \citet{muskat_1934} and later from \citet{saffman_1959} and \citet{homsy_1987}, the experimental setup of Hele-Shaw cell by \citet{saffman_1986}, and the basic mathematical model has been initially developed to describe the physics of this phenomenon. The idea is to introduce a fluid between two parallel flat plates separated by an infinitesimally small gap. The governing equation of Hele-Shaw flows is identical to that of the inviscid potential flow and to the flow of fluid through a porous medium (Darcy's law). More recently work that has been done by \citet{howison_2000} and \citet{praud_2005} give an extensive description on the mathematical background of the Saffman $\&$ Taylor problem (also know as immiscible two-phase flow in Hele-Shaw cell).
